%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{xcolor}
% Bib
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}
%\usepackage[resetlabels]{multibib}
%\newcites{patent,art,arxiv,conf,misc}{{Patents},{Articles in Peer Reviewed Journals},{Preprints},{Publications in Conferences and Workshops}, {Abstracts and Technical Reports}}
\usepackage[backend=biber,sorting=ydnt]{biblatex}
\addbibresource[label=patents]{my_patents.bib}
\addbibresource[label=journals]{my_journals.bib}
\addbibresource[label=pubs]{my_pubs.bib}
\addbibresource[label=arxiv]{my_arxiv.bib}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-skyblue}
\setbool{acvSectionColorHighlight}{true}
%\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%\headersocialsep[\quad\textbar\quad]
%\setbool{acvSectionColorHighlight}{true}

\name{Deepak}{Baby}
\position{Applied Scientist{\enskip\cdotp\enskip}Amazon Alexa AGI}
%\address{42-8, Bangbae-ro 15-gil, Seocho-gu, Seoul, 00681, Rep. of KOREA}

\mobile{(+32) 0483 611 040}
\email{deepakbabycet@gmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
\github{deepakbaby}
\linkedin{deepakbaby}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{medium-id}
% \kaggle{kaggle-id}
%\googlescholar{69q7FOYAAAAJ&hl}{Google Scholar}
%% \firstname and \lastname will be used
%\googlescholar{googlescholar-id}{}
% \extrainfo{extra information}



\begin{document}

\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Deepak Baby~~~·~~~Curriculum Vitae}
  {\thepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Amazon Alexa AGI}
	{Applied Scientist}
	{Oct 2020 – Present}
	{Aachen, Germany.}
	{\begin{cvitems}
		\item {Working on developing state-of-the-art multi-modal large language models.}
		\item {Lead scientist in establishing incremental learning framework for Alexa ASR models for model freshness and hotfixing.}
		\item {Develop and maintain speech recognition models deployed in Alexa devices on multiple languages.}
		\item {Close collaboration with various engineering teams automating the Alexa ASR production model builds.}
		\item {Develop quick solutions for customer facing issues in production models.}
		\item {Extensive experience working with big data, developing machine learning models and continuously improving them for production deployment.}
		\end{cvitems}}
	\cventry
	{IDIAP Research Institute}
	{Post-doctoral Researcher}
	{May 2019 - June 2020}
	{Martigny, Switzerland.}
	{\begin{cvitems}
		\item{Post-doctoral research fellow in the SNSF project 'SHISSM' with Prof. Herv\`{e} Bourlard.}
		\item {Collaborated with several PhD students providing support and guidance on their research.}
		\item {Developed speech enhancement (denoising and dereverberation) approaches using variational and adversarial auto-encoders.}
		\end{cvitems}}
	\cventry
	{Ghent University}
	{Post-doctoral Researcher}
	{Feb 2017 - Apr 2019}
	{Ghent, Belgium.}
	{\begin{cvitems}
		\item {Post-doctoral research fellow in the ERC project 'RobSpear' with Prof. Sarah Verhulst.}
		\item {Developed neural network-based machine learning techniques for modelling and correcting hearing impairment.}
		\item {Seminal work on using neural networks for approximating computational auditory models and hearing aids.}
		\item {Patent on neural network-based computational auditory models and publications in Nature: Machine Intelligence and Nature Communications.}
		\item {The patent was eventually granted \$1M ERC funding for startup.}
		\end{cvitems}}
	\cventry
	{Nuance Communications Inc.}
	{Visiting Researcher}
	{Apr - Jun 2015}
	{Merelbeke, Belgium.}
	{\begin{cvitems}
		\item {Investigated the previously proposed exemplar-based speech enhancement approaches as front-end for Nuance's ASR tasks on automotive data.}
		\end{cvitems}}
	\cventry
	{Tampere University of Technology}
	{Visiting Researcher}
	{Jun - Aug 2013}
	{Tampere, Finland.}
	{\begin{cvitems}
		\item {Internship with Prof. Tuomas Virtanen, Audio Research Group, Dept. of Signal Processing.}
		\item {Investigated the use of Modulation Envelope features for feature enhancement to improve the noise robustness of Automatic Speech Recognition systems}
	\end{cvitems}}
	\cventry
	{KU Leuven}
	{Teaching Assistant}
	{2013 - 2016}
	{Leuven, Belgium..}
	{\begin{cvitems}
		\item {Conducted the exercise sessions for the course \emph{'Stochastic Signal and System Analysis'}.}
	\end{cvitems}}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{Doctor of Philosophy (PhD)}
	{KU Leuven}
	{Leuven, Belgium.}
        {2012 - 2016}
	{\begin{tabular}{l c l}
		\textbf{Thesis} & : & ~~\textit{Non-negative Sparse Representations for Speech Enhancement and Recognition}\\
		\textbf{Supervisor} & : & ~~Prof. Hugo Van hamme \\
		& & \\
	 \end{tabular}
	}
	\cventry
	{Master of Technology (M.Tech)}
	{IIT Bombay}
	{Mumbai, India.}
	{2010 - 2012}
	{\begin{tabular}{l c l}
		\textbf{Specialization} & : & ~~Communication and Signal Processing (GPA: 9.45/10) \\
		\textbf{Thesis} & : & ~~\textit{Extensions to Greedy Algorithms in Compressed Sensing}\\
		\textbf{Supervisor} & : & ~~Prof. Sibi Raj B Pillai \\
		& & \\
	 \end{tabular}
	}
	\cventry
	{Bachelor of Technology (B.Tech)}
	{College of Engineering}
	{Trivandrum, India.}
	{2005 - 2009}
	{\begin{tabular}{l c l}
		\textbf{Specialization} & : & ~~Electronics and Communication Engineering (GPA: 7.57/10) \\
	 \end{tabular}
	}
\end{cventries}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Skills}
\begin{cvskills}
   \cvskill{Programming} { Python, Tensorflow, PyTorch, MATLAB}
   \cvskill{Cloud Infrastructure and DevOps}{ AWS, SageMaker, Docker, CI/CD, GNU/Linux}
   \cvskill{Data Engineering} { PySpark, Pandas}
\end{cvskills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Academic Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Academic Service \& Supervision}
\cvsubsection{Mentoring interns and masters thesis students}
\begin{cvhonors}
\cvhonor
    {Alkis Koudounas} % Position
    {Intern project: Learning from AI feedback for LLMs} % Location
    {Amazon Alexa}
    {2024} % Date(s)
\cvhonor
    {Sungjun Han} % Position
    {Intern project: Incremental learning for ASR using residual adapters} % Location
    {Amazon Alexa}
    {2022} % Date(s)
\cvhonor
    {Arthur Van Den Broucke} % Position
    {MS Thesis: Deep learning techniques for individualized auditory profiles} % Location
    {Ghent University}
    {2019} % Date(s)
\cvhonor
    {Joris Verhaegen} % Position
    {MS Thesis: NMF-based reduction of background sounds in TV shows for ASR} % Location
    {KU Leuven}
    {2015} % Date(s)
\cvhonor
    {Shubham Sharma} % Position
    {Intern project: De-reverberation using non-negative matrix factorisation} % Location
    {KU Leuven}
    {2015} % Date(s)
\end{cvhonors}
\cvsubsection{Reviewing}
\begin{cvskills}
	\cvskill{Journals}{Nature: Machine Intelligence}
    \cvskill{}{IEEE Transactions on Audio, Speech and Language Processing}
    \cvskill{}{IEEE Transactions on Signal Processing}
	\cvskill{}{IEEE Signal Processing Letters}
\cvskill{}{Computer, Speech \& Language}
\cvskill{}{Speech Communication}
\cvskill{}{Trends in Hearing}
%\vspace*{5pt}
\cvskill{Conferences}{INTERSPEECH}
\cvskill{}{IEEE International Conference on Audio, Speech and Signal Processing}
\cvskill{}{IEEE International Conference on Multimedia and Expo}

\end{cvskills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Patents \& Publications}
%
%\href{Google Scholar}{https://scholar.google.com/citations?user=69q7FOYAAAAJ&hl=en}\\
\cvsubsection{Patents}
%
\begin{refsection}[patents]
    \nocite{*}
    \printbibliography[
    heading=none,
    sorting=ydnt
    ]
\end{refsection}
%
\cvsubsection{Peer Reviewed Journals}
%
\begin{refsection}[journals]
    \nocite{*}
    \printbibliography[
    heading=none,
    sorting=ydnt
    ]
\end{refsection}
%
\cvsubsection{Conferences \& Workshops}
%
\begin{refsection}[pubs]
    \nocite{*}
    \printbibliography[
    heading=none,
    sorting=ydnt
    ]
\end{refsection}
%
\cvsubsection{Preprints}
%
\begin{refsection}[arxiv]
    \nocite{*}
    \printbibliography[
    heading=none,
    sorting=ydnt
    ]
\end{refsection}
%
\cvsection{References}
\begin{cventries}
    \cventry
	{Assistant Professor, Ghent University}
	{Prof. Sarah Verhulst}
	{sarah.verhulst@ugent.be}
	{}
	{}
    \cventry
	{Assistant Professor, KU Leuven}
	{Prof. Hugo Van hamme}
	{hugo.vanhamme@kuleuven.be}
	{}
	{}

\end{cventries}
\end{document}
